Inference methods for extended latent Gaussian models

### 2022-10-07 src/docs_15-11-22-seminar/15-11-22-seminar.Rmd
Date for student seminar talk

---
title: Inference methods for extended latent Gaussian models
subtitle: Waterloo SAS Student Seminar Series
author: Adam Howes
institute: Imperial College London
date: October 2022
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---

>>>>

---
title: Inference methods for extended latent Gaussian models
subtitle: Waterloo SAS Student Seminar Series
author: Adam Howes
institute: Imperial College London
date: November 2022
bibliography: citations.bib
output:
  beamer_presentation:
    latex_engine: pdflatex
    highlight: haddock
    fig_width: 7 
    fig_height: 3
    includes:
        in_header: preamble.tex
---
